Effects of the body force on the evacuation dynamics

### 2019-12-20 paper.tex
modificacion delos diagramas de venn

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
    \subfloat[]{\includegraphics[width=0.40\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_2parameters.png}\label{venn_2parameters}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./venn_3parameters.png}\label{venn_3parameters}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}
